---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/README-"
)
set.seed(0)
```

# simdynet

The goal of simdynet is to simulate realistic dynamic sexual networks. 

## Installation

You can install simdynet from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("lwhittles/simdynet")
```

The package can then be loaded using:
```{r}
library(simdynet)
```

## Example

This is a basic example of usage. To generate a dynamic network in a population of size 1000, and such that the degree distribution over a year follows a power law distribution with exponent 1.8, we can use:
```{r,warning=F}
test <- sim_dynamic_sn(N = 1000, gamma = 1.8)
plot(test$dd,xlab = '',ylab = 'Degree distribution',log = 'xy')
```

## More information and getting help

<<<<<<< HEAD
For more detailed examples of how to use simdynet, see the vignettes [here](https://github.com/xavierdidelot/simdynet/tree/master/vignettes).
=======
For more detailed examples of how to use simdynet, see the vignette [here](https://github.com/lwhittles/simdynet/tree/master/vignettes).
>>>>>>> d769c5fd3d2aa68ff7a4f2f44d9687d2efb2798a
See also the help included in the package using the R command
`help(package='simdynet')`. 

If you have any problem or question please create an issue [here](https://github.com/lwhittles/simdynet/issues) 
or get in touch by emailing `l.whittles14@imperial.ac.uk` or `xavier.didelot@gmail.com`
