---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/README-"
)
set.seed(0)
```

# simplasex

The goal of simplasex is to simulate realistic dynamic sexual networks. 

## Installation

You can install simplasex from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("lwhittles/simplasex")
```

The package can then be loaded using:
```{r}
library(simplasex)
```

## Example

This is a basic example of usage. 
```{r}
test <- sim_dynamic_sn(N = 1e3, gamma = 1.8)
plot(test$dd,xlab = '',ylab = 'Degree distribution',log = 'xy')
```

## More information and getting help

For more detailed examples of how to use simplasex, see the vignettes [here](https://github.com/xavierdidelot/simplasex/tree/master/vignettes).
See also the help included in the package using the R command
`help(package='simplasex')`. 

If you have any problem or question please create an issue [here](https://github.com/lwhittles/simplasex/issues) 
or get in touch by emailing `l.whittles14@imperial.ac.uk` or `xavier.didelot@gmail.com`
